Btech Project - Progress Diary

### 2017-07-29 Work_report/Daily_progress/work_progress_daily.tex
Updating daily work progress with bib file

>>>>

\subsubsection{July 27 : Thursday}
Accomplished :
\begin{itemize}
\item Completed reading all the papers and joting down main points of the paper.
\item Meeting with Sayan (main points written below):
  \begin{itemize}
  \item Video Co-segmentation hasn't been worked on by the Vision community yet.
  \item The main aim is to make an end-to-end model using RNN.
  \item To circumvent problems of vanishing gradients, we can use LSTM. But for our problem, even LSTM might not suffice.
  \item Hence we can use Memory Augmented LSTM, which should be able to take care of the vanishing gradients.
  \item There is no big datasets for the purpose of Video Co-segmentation. Hence we can look at Weakly unsupervised learning techniques to circumvent this problem.
  \item Need to read 5 papers at the earliest (by Monday). \cite{DBLP:journals/corr/SiamVJR16}, \cite{DBLP:journals/corr/JainZSS15}, \cite{PAVEL2017105}, \cite{DBLP:journals/corr/NohHH15}, \cite{DBLP:journals/corr/GulcehreCB17}
  \end{itemize}
\end{itemize}

\subsubsection{July 28 : Friday}
No work done

\subsubsection{July 29 : Saturday}
